---
title: 'Green Regional Path paper: Constructing Technology Spaces'
author: "Daniel S. Hain"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_notebook:
    df_print: paged
    toc: yes
    toc_depth: 3
    toc_float: yes
    number_sections: yes
    code_folding: hide
---

## Setup

```{r, setup, include=FALSE}
# Not sure if necessary... was an issue with a version conflict... try new version in the future again...
# devtools::install_version("RPostgres", version = "1.2.1", repos = "http://cran.us.r-project.org")

### general options
Sys.setenv(LANG = "en")
options("scipen" = 100, "digits" = 4) # override R's tendency to use scientific notation

### Clean workspace
rm(list=ls())
graphics.off()

### Load packages (maybe need to be installed first)
# Standard
library(tidyverse) # General DS toolkit
library(magrittr) # For advanced piping

# Databases
library(DBI) # GEneral R database interface
library(RPostgres) # PostgreSQL interface driver 
library(dbplyr) # for dplyr with databases

# Load functions
source("functions/functions_relatedness.R")
```

### Connect to database

```{r}
# Load script with variables
source("../variables.R")

# set up connection to existing PostgreSQL database, just plug in own details
con <- dbConnect(drv = RPostgres::Postgres(), 
                 dbname = var_dbname,
                 host = var_host, 
                 port = var_port,
                 user = var_user, 
                 password = var_password,
                 sslmode = 'require'
                 )

rm(var_dbname, var_host, var_password, var_port, var_user)
```

```{r}
# con %>% dbListTables() %>% sort()
```

# Defining parameters

```{r}
var_t_start <- 1990
var_t_end <- 2015
var_t_break <- 2000
```

# Load tables

```{r}
data_appln <- read_rds('../temp/tbl_region_appln.rds')
data_docdb_fam_cpc <- read_rds('../temp/tbl_region_docdb_fam_cpc.rds')
data_pers_appln <- read_rds('../temp/tbl_region_pers_appln.rds')
data_person <- read_rds('../temp/tbl_region_person.rds') %>% filter(nuts_level == 3)
data_tech_field <- read_rds('../temp/tbl_region_tech_field.rds') %>% mutate(techn_field_nr = techn_field_nr %>% as.character())
```

# Initial data cleaning

# Restrict by inventors only

```{r}
# Filter for only inventors
data_invt_appln <-data_pers_appln %>%
  filter(invt_seq_nr > 0)

data_applt_appln <-data_pers_appln %>%
  filter(applt_seq_nr > 0)
```

```{r}
# Filter applications and persons
data_appln %<>% semi_join(data_invt_appln, by = 'appln_id')
data_person %<>% semi_join(data_invt_appln, by = 'person_id')
```

## Restrict patent applications (families, years...)

```{r}
# Limit timeframe,
data_appln %<>%
  # filter(granted == 'Y') %>% # only granted patents
  filter(appln_filing_year >= var_t_start,
         appln_filing_year <= var_t_end) 
```


```{r}
# only include first patent per docdb family
data_appln %<>%
  group_by(docdb_family_id) %>%
    slice_min(order_by = appln_filing_date, n = 1, with_ties = FALSE) %>%
  ungroup() 
```

## Final application preprocessing

```{r}
# Create period tag
data_appln %<>%
  mutate(period = ((appln_filing_year >= var_t_break) + 1) %>% as.numeric() %>% as.character()) 
```


## Filter all other datasets

```{r}
data_invt_appln %<>% inner_join(data_appln %>% select(appln_id, appln_filing_year, Y_tag), by = 'appln_id')

data_docdb_fam_cpc %<>% semi_join(data_appln, by = 'docdb_family_id')
data_invt <- data_person %>% semi_join(data_invt_appln, by = 'person_id')
data_tech_field %<>% semi_join(data_appln, by = 'appln_id')
```

## Weight Persons

```{r}
data_invt_appln  %<>%
  group_by(appln_id) %>%
  mutate(n_inv = n()) %>%
  ungroup() %>%
  mutate(weight_frac = 1/n_inv) 
```

# Technology space (By technology classes)

```{r}
techn_field_names <- read_csv("../input/ipc_technology.csv") %>%
  select(field_nr, sector, field_name) %>%
  distinct(field_nr, .keep_all = TRUE) %>%
  rename(techn_field_nr = field_nr,
         techn_field_sector = sector,
         techn_field_name = field_name) %>%
  arrange(techn_field_nr) 
```

## Create Relatedness matrix

```{r}
# devtools::install_github("PABalland/EconGeo", force = T)
library(EconGeo)
```

```{r}
mat_tech <- create_sparse_matrix(i = data_tech_field %>% pull(appln_id),
                                       j = data_tech_field %>% pull(techn_field_nr),
                                       weight = data_tech_field %>% pull(weight),
                                       projection = 'j',
                                       sparse = FALSE)
```

```{r}
mat_tech %<>% relatedness(method = "cosine")
```

## Technology Space

```{r}
library(tidygraph)
library(ggraph)
```

```{r}
g_tech <- mat_tech %>% as_tbl_graph(directed = FALSE) %N>%
  left_join(techn_field_names %>% mutate(techn_field_nr = techn_field_nr %>% as.character()), by = c("name" = "techn_field_nr")) %>%
  mutate(dgr = centrality_eigen(weights = weight)) %E>%
  filter(weight >= mean(weight))
```



## Regional specialization

```{r}
region_tech <- data_appln %>%
  select(appln_id, appln_filing_year, period, Y_tag) %>%
  left_join(data_tech_field, by = 'appln_id') %>%
  left_join(data_invt_appln %>% select(appln_id, person_id, nuts, n_inv), by = 'appln_id') %>%
  mutate(weight_frac = weight / n_inv)
```

# Regional path identification

```{r}
region_RTA <- region_tech %>%  
  drop_na(Y_tag, nuts, techn_field_nr, period) %>%
  # Summing weights of non-Y and Y tagged 
  group_by(Y_tag, nuts, techn_field_nr, period) %>%
  summarise(n_tech_region = sum(weight_frac, na.rm = TRUE)) %>%
  ungroup() %>%
  # Calculate location quotient
    group_by(Y_tag, period) %>%
    mutate(n = sum(n_tech_region, na.rm = TRUE)) %>%
  ungroup() %>%
  group_by(Y_tag, period, nuts) %>%
    mutate(n_region = sum(n_tech_region, na.rm = TRUE)) %>%
  ungroup() %>%
  group_by(Y_tag, period, techn_field_nr) %>%
    mutate(n_tech = sum(n_tech_region, na.rm = TRUE)) %>%
  ungroup() %>%
  mutate(rta = ((n_tech_region / n_region) / (n_tech / n)) %>% round(2),
         rta_bin = (rta >= 1) %>% as.numeric() ) %>%
  # Replace NAs
  replace_na(list(rta = 0, rta_bin = 0, n_region = 0, n_tech = 0, n_tech_region = 0, n = 0)) %>%
  complete(Y_tag, nuts, techn_field_nr, period, fill = list(rta = 0, rta_bin = 0, n_region = 0, n_tech = 0, n_tech_region = 0, n = 0))
```
<!---

# Get applicants

Note: This is only the applicants for patents filed by inventors 
Note2: DO THAT SOMEWHERE EARLIER

```{r}
tbl_appln <- tbl(con, 'tls201_appln')
tbl_pers_appln <- tbl(con, 'tls207_pers_appln') 
tbl_person <- tbl(con, 'tls206_person')
```


```{r}
tbl_applt_list <- tbl_pers_appln %>%
  filter(applt_seq_nr > 0) %>%
  select(-applt_seq_nr, invt_seq_nr) %>%
  semi_join(data_appln %>% select(appln_id), by = 'appln_id', copy = TRUE) %>%
  distinct(person_id) %>%
  compute()
```

```{r}
# TODO: Also merge in Y-tag and year
tbl_applt_appln_all <- tbl_pers_appln %>%
  semi_join(tbl_applt_list, by = 'person_id') %>% 
  left_join(tbl_appln %>% select(appln_id, appln_filing_year), by = 'appln_id') %>%  
  compute()
```

```{r}
tbl_applt <- tbl_person %>%
  semi_join(tbl_applt_list, by = 'person_id') %>%
  compute()
```
--->



# Save all

```{r}
# SQL tables (Do that earlier.....)
#tbl_applt %>% collect() %>% write_rds('../temp/data_applt.rds')
#tbl_applt_appln_all %>% collect() %>% write_rds('../temp/data_applt_appln_all.rds')

# Regular tables
data_appln %>% write_rds('../temp/data_appln.rds')

data_invt %>% write_rds('../temp/data_invt.rds')
data_invt_appln  %>% write_rds('../temp/data_invt_appln.rds')

data_docdb_fam_cpc %>% write_rds('../temp/data_docdb_fam_cpc.rds')
data_tech_field %>% write_rds('../temp/data_tech_field.rds')

# Adittional ones
g_tech %>% write_rds('../temp/g_tech.rds')
region_RTA %>% write_rds('../temp/region_RTA.rds')
region_tech %>% write_rds('../temp/region_tech.rds')
```

```{r}
sessionInfo()
```

