---
title: 'Green Regional Path paper: Constructing Technology Spaces'
author: "Daniel S. Hain"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_notebook:
    df_print: paged
    toc: yes
    toc_depth: 3
    toc_float: yes
    number_sections: yes
    code_folding: hide
---

## Setup

```{r, setup, include=FALSE}
# Not sure if necessary... was an issue with a version conflict... try new version in the future again...
# devtools::install_version("RPostgres", version = "1.2.1", repos = "http://cran.us.r-project.org")

### general options
Sys.setenv(LANG = "en")
options("scipen" = 100, "digits" = 4) # override R's tendency to use scientific notation

### Clean workspace
rm(list=ls())
graphics.off()

### Load packages (maybe need to be installed first)
# Standard
library(tidyverse) # General DS toolkit
library(magrittr) # For advanced piping

# Databases
library(DBI) # GEneral R database interface
library(RPostgres) # PostgreSQL interface driver 
library(dbplyr) # for dplyr with databases

# Load functions
source("functions/functions_relatedness.R")
```

### Connect to database

```{r}
# Load script with variables
source("../variables.R")

# set up connection to existing PostgreSQL database, just plug in own details
con <- dbConnect(drv = RPostgres::Postgres(), 
                 dbname = var_dbname,
                 host = var_host, 
                 port = var_port,
                 user = var_user, 
                 password = var_password,
                 sslmode = 'require'
                 )

rm(var_dbname, var_host, var_password, var_port, var_user)
```

```{r}
# con %>% dbListTables() %>% sort()
```

```{r}
tbl_nuts <- tbl(con, 'tls904_nuts')
#tbl(con, 'tls902_ipc_nace2') #  TODO: CHeck why not included in our PATSTAT
```


# Defining parameters

```{r}
var_t_start <- 1985
var_t_end <- 2015
var_t_break <- 2000
```

# Load tables

```{r}
data_appln <- read_rds('../temp/tbl_region_appln.rds')

data_docdb_fam_cpc <- read_rds('../temp/tbl_region_docdb_fam_cpc.rds')
data_nace2 <- read_rds('../temp/tbl_region_appln_nace2.rds') 

data_pers_appln <- read_rds('../temp/tbl_region_pers_appln.rds')
data_person <- read_rds('../temp/tbl_region_person.rds') %>% filter(nuts_level == 3)
```

```{r}
data_appln %>% 
  count(Y_tag, appln_filing_year) %>%
  arrange(appln_filing_year, Y_tag) %>%
  ggplot(aes(y = n, x =appln_filing_year, col = Y_tag)) +
  geom_line()
```


# Initial data cleaning

## Restrict patent applications (families, years...)

```{r}
# Limit timeframe,
data_appln %<>%
  filter(granted == 'Y') #%>% # only granted patents
  #filter(appln_filing_year >= var_t_start,
        # appln_filing_year <= var_t_end) 
```


```{r}
# only include first patent per docdb family
data_appln %<>%
  group_by(docdb_family_id) %>%
    slice_min(order_by = appln_filing_date, n = 1, with_ties = FALSE) %>%
  ungroup() 
```

## Final application preprocessing

```{r}
# Create period tag
data_appln %<>%
  mutate(period = ((appln_filing_year >= var_t_break) + 1) %>% as.numeric() %>% as.character()) 
```

## Filter all datasets

```{r}
data_pers_appln %<>% inner_join(data_appln %>% select(appln_id, appln_filing_year, Y_tag), by = 'appln_id')
data_person %<>% semi_join(data_pers_appln, by = 'person_id')

data_docdb_fam_cpc %<>% semi_join(data_appln, by = 'docdb_family_id')
data_nace2 %<>% semi_join(data_appln, by = 'appln_id')
```


# Technology space (By technology classes)

## NACE 

```{r}
list_nace2 <- read_csv("../input/list_nace2.csv") %>%
  select(Level, Code, Description) %>%
  rename(level = Level,
         nace2_code = Code,
         nace2_name = Description) %>%
  mutate(nace_sec = ifelse(level == 1, nace2_code, NA),
         nace_div = ifelse(level == 2, nace2_code, NA),
         nace_group = ifelse(level == 3, nace2_code, NA),
         nace_class = ifelse(level == 4, nace2_code, NA)) %>%
  fill(nace_sec, nace_div, nace_group, nace_class, .direction = 'down') %>%
    mutate(nace_sec_name = ifelse(level == 1, nace2_name, NA),
         nace_div_name = ifelse(level == 2, nace2_name, NA),
         nace_group_name = ifelse(level == 3, nace2_name, NA),
         nace_class_name = ifelse(level == 4, nace2_name, NA)) %>%
    fill(nace_sec_name, nace_div_name, nace_group_name, nace_class_name, .direction = 'down') 
```


```{r}
data_nace2 %<>% 
  mutate(nace_div = nace2_code %>% str_sub(1, 2),
         nace_group = nace2_code %>% str_sub(1, 4),
         nace_class = nace2_code %>% str_sub(1, 5)) %>%
  left_join(list_nace2 %>% filter(level == 2) %>% select(nace_div, nace_sec), by = 'nace_div')
```

## Create Relatedness matrix

```{r}
# devtools::install_github("PABalland/EconGeo", force = T)
library(EconGeo)
```

```{r}
mat_tech <- create_sparse_matrix(i = data_nace2 %>% pull(appln_id),
                                       j = data_nace2 %>% pull(nace_group),
                                       weight = data_nace2 %>% pull(weight),
                                       projection = 'j',
                                       sparse = FALSE)
```

```{r}
mat_tech %<>% relatedness(method = "cosine")
```

## Technology Space

```{r}
library(tidygraph)
library(ggraph)
```

```{r}
g_tech <- mat_tech %>% as_tbl_graph(directed = FALSE) %N>%
  left_join(list_nace2 %>% filter(level == 3) %>% select(nace_group, nace_sec_name, nace_group_name), by = c('name' = 'nace_group')) %>%
  mutate(dgr = centrality_eigen(weights = weight)) %E>%
  filter(weight >= mean(weight))
```

```{r}
g_tech %N>% as_tibble() 
```

TODO: Repolace the NAs driven by categorization on class level


## Regional specialization

```{r}
region_tech <- data_appln %>%
  select(appln_id, appln_filing_year, period, Y_tag) %>%
  left_join(data_nace2 %>% select(appln_id, nace_group, weight), by = 'appln_id') %>%
  left_join(data_pers_appln %>% select(appln_id, person_id, nuts, n_inv), by = 'appln_id') %>%
  mutate(weight_frac = weight / n_inv)
```

# Regional path identification

```{r}
region_RTA <- region_tech %>%  
  drop_na(Y_tag, nuts, nace_group, period) %>%
  # Summing weights of non-Y and Y tagged 
  group_by(Y_tag, nuts, nace_group, period) %>%
  summarise(n_tech_region = sum(weight_frac, na.rm = TRUE)) %>%
  ungroup() %>%
  # Calculate location quotient
    group_by(Y_tag, period) %>%
    mutate(n = sum(n_tech_region, na.rm = TRUE)) %>%
  ungroup() %>%
  group_by(Y_tag, period, nuts) %>%
    mutate(n_region = sum(n_tech_region, na.rm = TRUE)) %>%
  ungroup() %>%
  group_by(Y_tag, period, nace_group) %>%
    mutate(n_tech = sum(n_tech_region, na.rm = TRUE)) %>%
  ungroup() %>%
  mutate(rta = ((n_tech_region / n_region) / (n_tech / n)) %>% round(2),
         rta_bin = (rta >= 1) %>% as.numeric() ) %>%
  # Replace NAs
  replace_na(list(rta = 0, rta_bin = 0, n_region = 0, n_tech = 0, n_tech_region = 0, n = 0)) %>%
  complete(Y_tag, nuts, nace_group, period, fill = list(rta = 0, rta_bin = 0, n_region = 0, n_tech = 0, n_tech_region = 0, n = 0))
```
<!---

# Get applicants

Note: This is only the applicants for patents filed by inventors 
Note2: DO THAT SOMEWHERE EARLIER

```{r}
tbl_appln <- tbl(con, 'tls201_appln')
tbl_pers_appln <- tbl(con, 'tls207_pers_appln') 
tbl_person <- tbl(con, 'tls206_person')
```


```{r}
tbl_applt_list <- tbl_pers_appln %>%
  filter(applt_seq_nr > 0) %>%
  select(-applt_seq_nr, invt_seq_nr) %>%
  semi_join(data_appln %>% select(appln_id), by = 'appln_id', copy = TRUE) %>%
  distinct(person_id) %>%
  compute()
```

```{r}
# TODO: Also merge in Y-tag and year
tbl_applt_appln_all <- tbl_pers_appln %>%
  semi_join(tbl_applt_list, by = 'person_id') %>% 
  left_join(tbl_appln %>% select(appln_id, appln_filing_year), by = 'appln_id') %>%  
  compute()
```

```{r}
tbl_applt <- tbl_person %>%
  semi_join(tbl_applt_list, by = 'person_id') %>%
  compute()
```
--->



# Save all

```{r}
# Lists
list_nace2 %>% write_rds('../temp/list_nace2.rds')

# Regular tables
data_appln %>% write_rds('../temp/data_appln.rds')

data_person %>% write_rds('../temp/data_person.rds')
data_pers_appln  %>% write_rds('../temp/data_pers_appln.rds')

data_docdb_fam_cpc %>% write_rds('../temp/data_docdb_fam_cpc.rds')
data_nace2 %>% write_rds('../temp/data_nace2.rds')

# Adittional ones
g_tech %>% write_rds('../temp/g_tech.rds')
region_RTA %>% write_rds('../temp/region_RTA.rds')
region_tech %>% write_rds('../temp/region_tech.rds')
```

```{r}
sessionInfo()
```

